---
title: "Bayesian Statistics HW 1"
author: "Ben"
date: "August 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#2.4. EXERCISES

Exercise 2.1. [Purpose: To get you actively manipulating mathematical models of probabilities.]

Suppose we have a four-sided die from a board game. On a tetrahedral die, each face is an equilateral triangle.When you roll the die, it lands with one face down and the other three faces visible as a three-sided pyramid. The faces are numbered 1-4, with the value of the bottom face printed (as clustered dots) at the bottom edges of all three visible faces. Denote the value of the bottom face as x. Consider the following three mathematical descriptions of the probabilities of x. 

For each model, determine the value of p(x) for each value of x. Describe in words what kind of bias (or lack of bias) is expressed by each model.

```{r, echo=TRUE,warning=FALSE,message=FALSE}
library(ggplot2)
library(knitr)
ggplot(transform(data.frame(x=c(1:4)), y=rep(0.25)), aes(x, y)) + 
    geom_bar(stat="identity")
```
```{r echo = FALSE, results='asis'}
kable(transform(data.frame(x=c(1:4)), y=rep(0.25)),caption = "Model A: p(x) = 1/4",align = "c")
```

Model A displays no bias towards any values of x.

#

```{r, echo=TRUE}
ggplot(transform(data.frame(x=c(1:4)), y=rep(x/10)), aes(x, y)) + 
    geom_bar(stat="identity")
```
```{r echo = FALSE, results='asis'}
kable(transform(data.frame(x=c(1:4)), y=rep(x/10)),caption = "Model A: p(x) = x/10",align = "c")
```

Model B displays bias for higher values of x, such that higher values of x have a higher probability of occuring.

#

```{r, echo=TRUE}
ggplot(transform(data.frame(x=c(1:4)), y=rep(12/(25*x))), aes(x, y)) + 
    geom_bar(stat="identity")
```
```{r echo = FALSE, results='asis'}
kable(transform(data.frame(x=c(1:4)), y=rep(12/(25*x))),caption = "Model C: p(x) = 12/(25x)",align = "c")
```

Model C displays bias for lower values of x, such that lower values of x have a higher probability of occuring.

#

Exercise 2.2. [Purpose: To get you actively thinking about how data cause credibilities to shift.] Suppose we have the tetrahedral die introduced in the previous exercise, along with the three candidate models of the die’s probabilities. Suppose that initially, we are not sure what to believe about the die. On the one hand, the die might be fair, with each face landing with the same probability. On the other hand, the die might be biased, with the faces that have more dots landing down more often (because the dots are created by embedding heavy jewels in the die, so that the sides with more dots are more likely to land on the bottom). On yet another hand, the die might be biased such that more dots on a face make it less likely to land down (because maybe the dots are bouncy rubber or protrude from the surface). So, initially, our beliefs about the three models can be described as p(A) = p(B) = p(C) = 1/3. Now we roll the die 100 times and find these results: #1’s = 25, #2’s = 25, #3’s = 25, #4’s = 25. Do these data change our beliefs about the models? Which model now seems most likely? Suppose when we rolled the die 100 times we found these results: #1’s = 48, #2’s = 24, #3’s = 16, #4’s = 12. Now which model seems most likely?

Our initial beliefs give an equal weighting to each of our candidate models. After rolling the die 100 times and getting #1's = 25, #2's = 25, #3's = 25, and $4's = 25, we can shift our beliefs to model A, given the empirical data we collected mirrors the hypothesized data model A would generate.

```{r, echo=TRUE,warning=FALSE,message=FALSE}
ggplot(transform(data.frame(x=c(1:4)), y=rep(25)), aes(x, y)) + 
    geom_bar(stat="identity")
```
```{r echo = FALSE, results='asis'}
kable(transform(data.frame(x=c(1:4)), y=rep(25)),caption = "Empirical data demonstrate evidence for candidate model A",align = "c")
```

If we were to instead find #1's = 48, #2’s = 24, #3’s = 16, and #4’s = 12, we would have evidence in support of candidate model C, given the empirical data match what model C might generate.

```{r, echo=TRUE,warning=FALSE,message=FALSE}
ggplot(transform(data.frame(x=c(1:4)), y=c(48,24,16,12)), aes(x, y)) + 
    geom_bar(stat="identity")
```
```{r echo = FALSE, results='asis'}
kable(transform(data.frame(x=c(1:4)), y=c(48,24,16,12)),caption = "Empirical data demonstrate evidence for candidate model A",align = "c")



